% INTRODUCTION

\todo[inline,color=yellow!40]{The introduction is one of the most important pieces of your thesis.  Here is a place for you to introduce the problem(s) on which you have worked and place them in the larger context of your field. You should aim to ensure that this section is completely understandable to virtually anyone - and certainly anyone with a sophomore-level grasp of physics.  Presumably, this will include references to the literature.
\\
In addition to setting your work into context, a second good idea for your introduction is to give a short outline for what the rest of your thesis will discuss.  This is often done in the closing paragraph(s) of the introduction with sentences like ``In the following chapters \ldots " and ``Chapter 2 discusses \ldots"  Tremendous detail is not required in this outline, but rather just a brief road map for the rest of the document.}

\section{X-ray Absorption Spectroscopy}
\todo[color=green!40, inline]{I want to describe the problem we're trying to solve in this section. So I want to motivate the problem by describing XAFS a little so I can describe the limitations of XANES and why this project is useful. More in-depth explanations can be placed in chapter 2}

X-ray absorption spectroscopy measures the absorption of high-energy photons by a sample as a function of energy \cite{gardenghi2012synchrotron}. The attenuation, or change in transmitted light intensity as a result of inelastic processes, is characterized by the Beer-Lambert Law (\ref{BeerLambert}). For an incident beam of intensity $I_0$, the transmitted intensity after interacting with an \todo[color=blue!40]{pick one} attenuation/absorption 
coefficient of $ \mu $ and a sample of thickness $ x $ is: 

\begin{equation}
    \label{BeerLambert}
    I = I_0 e^{-\mu x}
\end{equation}

Above the absorption edge, the condensced state has characteristic absorption jumps where the incident photon's energy matches the binding energy of a core electron. At this energy, nearly all the photon's energy is absorbed by the core electron, resulting in the characteristic absorption-edges first observed in 1920 \cite{fricke1920, hertz1920ueber}.

\subsection{Synchrotron Radiation}
\todo[color=orange!60, inline]{I'm not sure where this will end up going, but somewhere I'll have to write about the origin of synchrotron radiation}

Synchrotron radiation was first observed by General Electric in Schenectady, New York \cite{firstSynchrotronRadPaper}. Initially just a side effect of particle accelerator experiments, it has since grown to be an important and powerful source of high-energy electromagnetic radiation for structural determination. Compared to lab-scale x-ray generation for diffraction experiments, arguably the most important benefit of synchrotron radiation is its high brilliance. Synchrotron radiation creates a highly collimated beam of photons characterized by small divergence and spatial coherence. Additionally, synchrotron radiation is tunable across a wide spectrum (microwaves to hard X-rays)\todo[color=green!50]{frequency range?} and capable of high flux, useful for short time-scale-dependent experiments or weak scatterers. Synchrotron radiation can be produced in a pulsed structure, and the incoming photons are highly polarized, either linearly or circularly depending on where the measurement system lies with respect to the plane of the synchrotron. \todo[color=yellow!40]{wordy}

\subsection{XAFS}
X-ray Absorption Fine-Structure (XAFS) spectroscopy refers to the study of absorption spectra created from high-intensity x-ray interactions. As the energy of the incident radiation is increased, the photon's energy will eventually match the binding energy of a core-level electron. As a result, an "edge" in the spectrum will be observed. The location of these edges depends on the chemical and physical structure, as well as the electronic and vibrational state of the material, creating characteristic absorption oscillations.

(Here's a good source to cite a bunch: the 2000 review of XAFS
\cite{rehrXAFS2000review})
\cite{newville2014fundamentals}

\textit{absorption edges like fingerprints to identify elements. in 1920 Frische and Hertz observed peak shape, and 40 years later it was learned that this shape can be used to probe the short-range order.1971 e.a. Sterne expalin this effect. Fermi's golden rule. The inelastic interactions of the photon are related to characteristic energies. When the photon energies match the energy difference from the core-electron state to the first unoccupied level, the photon can be fully absorbed (before that only partially absorbed.)}


\begin{equation}
    \label{Victoreen}
    \mu(E) = aE^{-3} + bE^{-4}
\end{equation}

\begin{equation}
    \label{FermisGoldenRule}
    % Fermi's GOlden Rule for a one e- approximation
    \mu(E) \varpropto \sum_{f}^{E_f > E_F} \left\lvert \left\langle f \lvert H_{int} \rvert i \right\rangle \right\rvert ^2 \delta (E - E_F - Ef)  
\end{equation}

\subsection{EXAFS}
Extended X-ray Absorption Fine Structure (EXAFS)


\subsection{XANES}

\section{Disorder in XAFS}

\section{Nanoparticles?}
\section{Machine Learning?}

Probably want to talk about these papers in this section \cite{timoshenko2018neural} \cite{Timoshenko2017}.
\section{Outline of the Thesis}
Building off the historical context of measuring disordered nanoparticles in XANES spectra, this thesis begins with an in-depth description of 
